%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Bryan Oliveira} \\ \vspace{1pt}
    \small
    \href{https://github.com/BryOliveira}{\raisebox{-0.1\height}{\faGithub \scriptsize} \underline{\smash{github.com/BryOliveira}}} ~
    \href{mailto:bryoliveira2004@gmail.com}{\raisebox{-0.1\height}{\faEnvelope \scriptsize} \underline{\smash{bryoliveira2004@gmail.com}}} ~
    \href{https://linkedin.com/in/bryan-r-oliveira/}{\raisebox{-0.1\height}{\faLinkedin \scriptsize} \underline{\smash{linkedin.com/in/bryan-r-oliveira}}}
    \vspace{-12pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Institute of Technology}{Jun. 2026}
      {Bachelor of Science in Computer Science $|$ GPA: 3.7}{Pasadena, CA}
  \resumeSubHeadingListEnd
\vspace{-14pt}

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-4pt, parsep=5pt]
                \item\small Object-Oriented Programming
                \item Algorithms and Complexity Analysis
                \item Data Structures
                \item Software Design
                \item Systems Programming
                \item Deep Learning Systems
                \item Relational Databases
                \item Differential Equations
                \item Probability Models
                \item Web Development
                \item GPU Programming
                \item Machine Learning and Data Mining
                \item Integrated Circuits
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

\vspace{-4pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, C, C++, Java, HTML, CSS, MySQL, MATLAB} \\
     \textbf{Frameworks/Libraries}{: React, Flask, PyTorch, sklearn, pandas, Matplotlib, NumPy, CUDA} \\
     \textbf{DevOps \& Other}{: Git, VSCode, Linux, WSL, LaTeX}
    }}
 \end{itemize}
 \vspace{-18pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Navy Federal Credit Union}{Jun. 2024 -- Sep. 2024}
      {Software Engineer Intern}{Vienna, VA}
      \resumeItemListStart
        \resumeItem{Engineered internal SharePoint portals for the Security, Financial, and Fraud teams consisting of 60+ users cutting average onboarding time by about 15\%.}
        \resumeItem{Designed 30+ custom UI icons and infographics using HTML, CSS, and JavaScript, strengthening branding and enhancing UI/UX cohesion.}
        \resumeItem{Spearheaded development of a JavaScript org-chart creation web app to replace static diagrams and to enable real-time structural updates for all $\sim$24,000 employees.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-7pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Affor-db: House Affordability Database Application} $|$ \emph{Python, MySQL}}{Feb. -- Mar. 2025}
          \resumeItemListStart
            \resumeItem{Co-created a CLI tool integrating MySQL schemas with housing, mortgage, and job market datasets to generate personalized affordability metrics across 450+ jobs and 350+ companies across all U.S. states.}
            \vspace{-18pt}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Leggies: Physics-Based Fighting Game} $|$ \emph{C, GitLab}}{May -- Jun. 2024}
          \resumeItemListStart
            \resumeItem{Constructed a 1v1 multiplayer fighting game with collision detection, sprite animation, and real-time combat logic.}
            \resumeItem{Developed a custom physics engine in C for applying object-oriented design patterns for entity behavior.}  
            \resumeItem{Collaborated with a 3-person team using GitLab, resolving merge conflicts and optimizing shared code structure.}
          \resumeItemListEnd
          \vspace{-18pt}
      \resumeProjectHeading
          {\textbf{Secure Password Recovery Tool} $|$ \emph{Python, Flask, HTML, CSS, MySQL}}{Dec. 2023}
          \resumeItemListStart
            \resumeItem{Developed a secure password reset system using one-time hashed token authentication, enabling recovery for 180+ users.}
            \resumeItem{Integrated Flask with a MySQL user database and front-end interface for seamless end-to-end user password recovery.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15.5pt}

%-----------INVOLVEMENT---------------
\section{Leadership / Extracurriculars}
    \resumeSubHeadingListStart
        \resumeSubheading{Caltech Hispanic and Latino Association (SHPE Chapter)}{Jun. 2024 -- Present}{Social Director}{Pasadena, CA}
        \resumeItemListStart
          \resumeItem{Directed community-building events, strengthening networks for Caltech’s 170+ Latine undergraduates.}
          \resumeItem{Coordinated with 8 other executive committee members and many cross-campus leaders to advance diversity, equity, and inclusion initiatives.}
        \resumeItemListEnd
        \resumeSubheading{Caltech Sunday League Soccer}{Feb. 2023 -- Present}{Captain}{Pasadena, CA}
        \resumeItemListStart
          \resumeItem{Lead and manage a 31-member undergraduate team, coordinating with Caltech's recreation director on scheduling and compliance.}
        \resumeItemListEnd
        \resumeSubheading{Caltech First-Year Success Research Institute}{Jul. 2023 -- Sep. 2023}{Peer Mentor}{Pasadena, CA}
        \resumeItemListStart
            \resumeItem{Orchestrated weekly social events for 48 incoming first-year students, fostering community and accelerating their college transition, earning a 100\% satisfaction rate in post-program surveys.}
            \resumeItem{Guided 10 students through bi-weekly check-ins, delivering personalized mentorship and academic/social support.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
